Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2017-05-10 cbm-rbd-paper.tex
timeline figure done

Now we can derive the adaptive and dynamic maintenance policy
that resembles a CBM policy.
Consider a set of evaluation time points $\tnow$.
Instead of determining a threshold for a degradation signal like in usual CBM approaches,
we determine, for each present time $\tnow$,
the adaptive and dynamic time span $\tausnow$ which gives the time from $\tnow$ until the optimal moment of maintenance.
Close to system startup, $\tausnow$ will be large;
but as components in the system age and some indeed fail over time,
$\tausnow$ will typically decrease.
%Let $\tprep$ be the time span needed to prepare maintenance work.
%Let $\tthresh$ be a threshold time span chosen for practical reasons.
%used to decide when maintenance is initiated, i.e.,
A preventive maintenance action is initiated
as soon as $\tausnow$ decreases below the time span to the next evaluation time.
%continuing to the the next evaluation point $\tnow$ would carry the risk 
%a time span chosen to reflect operational practicalities.
This dynamic and adaptive maintenance policy is described in more detail in Section~\ref{sec:operationalprocedure};
a flow chart for the policy is given in Figure~\ref{fig:procedure}.

@@

\begin{figure}
\centering
\begin{tikzpicture}
\node {exemplary timeline};
\end{tikzpicture}
\caption{***exemplary timeline sketch}
\label{fig:timeline}
\end{figure}

>>>>

Now we can derive the adaptive and dynamic maintenance policy
that resembles a CBM policy.
Figure~\ref{fig:timeline} shows two example time lines for the system,
starting each with a new system (operational cycle) at t=0.

***explain figure, triggers 1, 2, 3***

Consider a set of evaluation time points $\tnow$.
Instead of determining a threshold for a degradation signal like in usual CBM approaches,
we determine, for each present time $\tnow$,
the adaptive and dynamic time span $\tausnow$ which gives the time from $\tnow$ until the optimal moment of maintenance.
Close to system startup, $\tausnow$ will be large;
but as components in the system age and some indeed fail over time,
$\tausnow$ will typically decrease.
%Let $\tprep$ be the time span needed to prepare maintenance work.
%Let $\tthresh$ be a threshold time span chosen for practical reasons.
%used to decide when maintenance is initiated, i.e.,
A preventive maintenance action is initiated
as soon as $\tausnow$ decreases below the time span to the next evaluation time.
%continuing to the the next evaluation point $\tnow$ would carry the risk 
%a time span chosen to reflect operational practicalities.
This dynamic and adaptive maintenance policy is described in more detail in Section~\ref{sec:operationalprocedure};
a flow chart for the policy is given in Figure~\ref{fig:procedure}.

@@

\begin{figure}
\centering
\begin{tikzpicture}
%[tausnow/.style={|-|, line width=0.5mm}]
[ tausnow/.style={line width=0.8mm},
  pfeil/.style={-latex', line width=0.5mm, shorten >=1mm}] 
\draw[-latex', very thick] (-0.2, -0.5) -- (5.5, -0.5) node[below] {$t$};
\draw (0, -0.4) -- (0, -0.6) node[below] {$0$};
\foreach \x in {1, 2, 3, 4, 5}
 {\draw (\x, -0.4) -- (\x, -0.6) node[below] {$0.\x$};
  \draw[dotted] (\x, -0.4) -- (\x, \x); }
\draw[thick, decorate, decoration=brace] (1, -1) -- (0, -1) node[midway,below] {$\delta$};
\draw[dashed] (0, 0) -- (5,5);
\draw[tausnow] (0  , 0  ) -- (2.3, 0  ) node[at start, left] {$\tau_*^{(0)}$};
\draw[tausnow] (1  , 1  ) -- (2.9, 1  ) node[at start, left] {$\tau_*^{(0.1)}$};
\draw[tausnow] (2  , 2  ) -- (4.2, 2  ) node[at start, left] {$\tau_*^{(0.2)}$};
\draw (2.4, -0.4) circle (0.8mm) edge[dotted] (2.4, 2.4);
%\node[draw,shape=diamond] (f1) at (2.4, -0.4) {}; % edge[dotted] (2.4, 2.4);
\draw[tausnow] (2.4, 2.4) -- (3.9, 2.4) node[at start, left] {$\tau_*^{(0.24)}$};
\draw[tausnow] (3  , 3  ) -- (4.4, 3  ) node[at start, left] {$\tau_*^{(0.3)}$};
\draw (3.6, -0.4) circle (0.8mm) edge[dotted] (3.6, 3.6);
\draw[tausnow] (3.6, 3.6) -- (4.3, 3.6) node[at start, left] {$\tau_*^{(0.36)}$};
\draw[tausnow] (4  , 4  ) -- (4.7, 4  ) node[at start, left] {$\tau_*^{(0.4)}$};
\node (box1) at (1,4) {\parbox{12ex}{\small preventive\\ replacement\\ at $\tnow = 0.4$\\ as $\tau_*^{(0.4)} < \delta$}};
\draw[pfeil] (box1) edge[out=20, in=120] (4,4);
\begin{scope}[xshift=7cm]
\draw[-latex', very thick] (-0.2, -0.5) -- (3.5, -0.5) node[below] {$t$};
\draw (0, -0.4) -- (0, -0.6) node[below] {$0$};
\foreach \x in {1, 2, 3}
 {\draw (\x, -0.4) -- (\x, -0.6) node[below] {$0.\x$};
  \draw[dotted] (\x, -0.4) -- (\x, \x); }
\draw[thick, decorate, decoration=brace] (1, -1) -- (0, -1) node[midway,below] {$\delta$};
\draw[dashed] (0, 0) -- (3,3);
\draw[tausnow] (0  , 0  ) -- (2.3, 0  ) node[at start, left] {$\tau_*^{(0)}$};
\draw[tausnow] (1  , 1  ) -- (2.9, 1  ) node[at start, left] {$\tau_*^{(0.1)}$};
\draw (1.4, -0.4) circle (0.8mm) edge[dotted] (1.4, 1.4);
\draw[tausnow] (1.4, 1.4) -- (2.8, 1.4) node[at start, left] {$\tau_*^{(0.14)}$};
\draw[tausnow] (2  , 2  ) -- (3.3, 2  ) node[at start, left] {$\tau_*^{(0.2)}$};
\draw[fill] (2.7, -0.4) circle (0.8mm) edge[dotted] (2.7, 2.7);
\node (box2) at (1,4) {\parbox{13ex}{\small corrective\\ replacement\\ at $\tnow = 0.27$\\ due to system failure}};
\draw[pfeil] (box2) edge[out=10, in=90] (2.7,2.7);
\end{scope}
\end{tikzpicture}
\caption{Two exemplary timelines for the suggested maintenance policy.
The horizontal bars depict, for subsequent times $\tnow$,
the time to the next economically optimal inspection $\tausnow$.
The times $\tnow$ for which $\tausnow$ is evaluated are
at regular intervals $\delta, 2\delta, 3\delta,\ldots$ (trigger 1),
and at the time of component failures (trigger 2),
marked by a circle on the time axis.
Failures that lead to the whole system failing (trigger 3) are marked by a filled circle.
The calculation of $\tausnow$ is described in detail in Section~***.}
\label{fig:timeline}
\end{figure}
